%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Programming Tutor} % Job title
    {Searsol} % Organization
    {Dublin, Ireland} % Location
    {Jun. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deliver group tutoring sessions in Python, HTML, CSS, and introductory computing concepts.}
        \item {Design engaging lessons focused on developing problem-solving, coding logic, and foundational programming skills for students of varying levels.}
        \item {Provide hands-on guidance in both front-end and back-end development principles, preparing students for further study or real-world applications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer (Student-Led Project)} % Job title
    {UCD Festival Volunteer Project} % Organization
    {Dublin, Ireland} % Location
    {May. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a full-stack CSO Report Generator using Flask backend, integrating CSO API and OpenAI API to automate data analysis and report generation.}
        \item {Developed and deployed a mobile-friendly web application, hosted online and designed to handle live user traffic (10 concurrent users).}
        \item {Managed end-to-end development including API integration, server deployment, and user interface design.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
